\documentclass[xcolor=pdftex,dvipsnames,table]{beamer}
\usecolortheme[accent=yellow,dark]{solarized}
\usepackage{etex}
\providecommand\thispdfpagelabel[1]{}
\usepackage{color}
\usepackage{xcolor}
\usepackage[latin1]{inputenc}
\usepackage[absolute,overlay]{textpos}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{times}
\usepackage{listings}
\usepackage{graphics}
\usepackage{framed}
\usepackage{etex}
\usepackage[all]{xy}
\usepackage{xspace,listings,ulem,tikz}
\usepackage[outline]{contour}
\contourlength{1.2pt}
\usepackage[square,sort,comma,numbers]{natbib}
\usepackage{hhline}
\setbeamertemplate{footline}[frame number]
\tikzset{
    onslide/.code args={<#1>#2}{% http://tex.stackexchange.com/a/6155/16595
        \only<#1>{\pgfkeysalso{#2}}
    },
    hideshow/.style args={<#1><#2>#3}{%
        onslide=<#1>{move to},
        onslide=<#2>{#3}
    }
}

\lstset{
         basicstyle=\small\ttfamily, % Standardschrift
         %numbers=left,               % Ort der Zeilennummern
         numberstyle=\tiny,          % Stil der Zeilennummern
         %stepnumber=2,               % Abstand zwischen den Zeilennummern
         numbersep=5pt,              % Abstand der Nummern zum Text
         tabsize=2,                  % Groesse von Tabs
         extendedchars=true,         %
         breaklines=true,            % Zeilen werden Umgebrochen
         keywordstyle=\color{solarized@magenta},
         stringstyle=\color{solarized@yan}\ttfamily,
         identifierstyle=\color{solarized@blue},
         commentstyle=\color{solarized@base01},
         emphstyle=\color{solarized@red},
         showspaces=false,           % Leerzeichen anzeigen ?
         showtabs=false,             % Tabs anzeigen ?
         xleftmargin=3pt,
         framexleftmargin=3pt,
         framexrightmargin=1pt,
         framexbottommargin=3pt,
         language=C++,
         %backgroundcolor=\color{lightgray},
         showstringspaces=false,      % Leerzeichen in Strings anzeigen ?        
         escapeinside=||
 }
\lstset{
  emph={REAL, DYADIC, LAZY_BOOLEAN}
}
 \usetikzlibrary{arrows}
 \usepackage{caption}
\DeclareCaptionFont{white}{\color{white}}
\DeclareCaptionFormat{listing}{\colorbox[cmyk]{0.43, 0.35, 0.35,0.01}{\parbox{\textwidth}{\hspace{15pt}#1#2#3}}}
\captionsetup[lstlisting]{format=listing,labelfont=white,textfont=white, singlelinecheck=false, margin=0pt, font={bf,footnotesize}}
\beamertemplatenavigationsymbolsempty
\newcommand{\N}{\ensuremath{\mathbb{N}}} 
\newcommand{\R}{\ensuremath{\mathbb{R}}} 
\newcommand{\RR}{\ensuremath{\mathbb{R}}} 
\newcommand{\C}{\ensuremath{\mathbb{C}}} 
\newcommand{\Q}{\ensuremath{\mathbb{Q}}} 
\newcommand{\Z}{\ensuremath{\mathbb{Z}}} 
\newcommand{\D}{\ensuremath{\mathbb{D}}}
\newcommand{\lb}{\mathrm{lb}}
\newcommand{\dy}{\mathrm{dy}}
\newcommand{\cc}{\texttt{C++}\xspace}
\newcommand{\bin}{\mathrm{bin}}
\newcommand{\irram}{\texttt{iRRAM}\xspace}
\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\sharpp}{\ensuremath{\#\mathcal P}\xspace}
\newcommand{\sharppu}{\ensuremath{\#{\mathcal P}_1}\xspace}
\newcommand{\fp}{\ensuremath{\mathcal{FP}}\xspace}
  \newcommand{\baana}{\code{BA\_ANA}\xspace}
  \newcommand{\anarect}{\code{ANA\_RECT}\xspace}
  \newcommand{\powerseries}{\code{POWERSERIES}\xspace}
  \newcommand{\poly}{\code{POLY}\xspace}
  \newcommand{\func}{\code{FUNC}\xspace}
  \newcommand{\real}{\code{REAL}\xspace}
  \newcommand{\complex}{\code{COMPLEX}\xspace}
  \newcommand{\temp}{\textcolor{red}}
  \newcommand{\seq}{\mathbf}
\newcommand{\fpu}{\ensuremath{\mathcal{FP}_1}\xspace}
\DeclareMathOperator{\dom}{\mathrm{dom}}
\newtheorem{conjecture}{Conjecture} 
\newtheorem{representation1}{Representation 1} 
\newtheorem{representation1b}{Representation 1'} 
\newtheorem{representation2}{Representation 2} 
\title[Analytic Continuation in iRRAM]{Analytic Continuation in \irram}
\author[A. Kawamura, F. Steinberg, H. Thies]{
		Akitoshi Kawamura, Florian Steinberg, Holger Thies 
}
\institute[JAIST]{
	Japan Institute of Science and Technology, Ishikawa Prefecture
}

\definecolor{solarized@base03}{HTML}{002B36}
\definecolor{solarized@base02}{HTML}{073642}
\definecolor{solarized@base01}{HTML}{586e75}
\definecolor{solarized@base00}{HTML}{657b83}
\definecolor{solarized@base0}{HTML}{839496}
\definecolor{solarized@base1}{HTML}{93a1a1}
\definecolor{solarized@base2}{HTML}{EEE8D5}
\definecolor{solarized@base3}{HTML}{FDF6E3}
\definecolor{solarized@yellow}{HTML}{B58900}
\definecolor{solarized@orange}{HTML}{CB4B16}
\definecolor{solarized@red}{HTML}{DC322F}
\definecolor{solarized@magenta}{HTML}{D33682}
\definecolor{solarized@violet}{HTML}{6C71C4}
\definecolor{solarized@blue}{HTML}{268BD2}
\definecolor{solarized@cyan}{HTML}{2AA198}
\definecolor{solarized@green}{HTML}{859900}
\begin{document}
\setbeamercolor{note}{fg=black,bg=lightgray} 
\date{July 21, 2015}
\frame{
\titlepage
}
\frame[<+->]{
\frametitle{Table of Contents}
\tableofcontents
}
\include{background}
\include{motivation}
\include{powerseries}
\include{implementation}
\begin{frame}

    \vspace{\fill}
\begin{beamercolorbox}[center,shadow=true,rounded=true]{note} 
        \huge Thank you!
\end{beamercolorbox}

    \vspace{\fill}
\end{frame} 
{
\makeatletter % to change template
    \setbeamertemplate{headline}[default] 
    \def\beamer@entrycode{\vspace*{-\headheight}} 
\makeatother
\begin{frame}{References}
\fontsize{6pt}{7.2}\selectfont 
\nocite{*}
\def\newblock{}
\bibliographystyle{abbrv}

\begin{thebibliography}{10}   

  \beamertemplatearticlebibitems
  \bibitem{6}
	Harvey Friedman,
    \newblock \emph{ The computational complexity of maximization and integration}, Adv. in Math. 53 (1984), no. 1, 80-98. MR 748898 (86c:03037)
  \beamertemplatearticlebibitems
  \bibitem{1}
	Akitoshi Kawamura, Norbert Th. M\"{u}ller, Carsten R\"{o}snick, and
Martin Ziegler
    \newblock \emph{Parameterized Uniform Complexity in Numerics:
from Smooth to Analytic, from NP-hard to Polytime}, pre-print (2012).

  \beamertemplatearticlebibitems
  \bibitem{7}
	Ker-I Ko,
    \newblock \emph{ Complexity theory of real functions}, Progress in Theoretical Computer Science, Birkh\"{a}user Boston Inc., Boston, MA, 1991.
MR 1137517 (93i:03057)

  \beamertemplatearticlebibitems
  \bibitem{8}
	Ker-I Ko,
    \newblock \emph{  On the Computational Complexity of Ordinary Differential Equations}, Information and Control 58(1-3): 157-194 (1983)


  \beamertemplatearticlebibitems
  \bibitem{2}
	Norbert Th. M\"{u}ller,
    \newblock \emph{ The \irram: Exact Real Arithmetic in C++}, Computability and Complexity in Analysis (2000) .

  \beamertemplatearticlebibitems
  \bibitem{Mul95}
	Norbert Th. M\"{u}ller,
    \newblock \emph{ Constructive aspects of analytic functions}, Computability
and Complexity in Analysis (Ker-I Ko and Klaus Weihrauch, eds.),
Informatik Berichte, vol. 190, FernUniversit\"{a}t Hagen, September
1995, CCA Workshop, Hagen, August 19-20, 1995, pp. 105-114.

  \beamertemplatearticlebibitems
  \bibitem{4}
	Norbert Th. M\"{u}ller,
    \newblock \emph{ Uniform Computational Complexity of Taylor Series}, ICALP 1987: 435-444

  \beamertemplatearticlebibitems
  \bibitem{5}
	Norbert Th. M\"{u}ller,
    \newblock \emph{ Polynomial Time Computation of Taylor Series}, Proc. 22 JAIIO - PANEL 1993

  \beamertemplatearticlebibitems
  \bibitem{9}
	Marian B. Pour-El and J. Ian Richards,
    \newblock \emph{ Computability in analysis
and physics}, Perspectives in Mathematical Logic, Springer-Verlag,
Berlin, 1989. MR 1005942 (90k:03062)
  \beamertemplatearticlebibitems
  \bibitem{11}
	Florian Steinberg,
    \newblock \emph{A type of Taylor series for the C++ library iRRAM for exact real arithmetic} (draft) last edited November 28, 2013
  \beamertemplatearticlebibitems
  \bibitem{10}
	Klaus Weihrauch,
    \newblock \emph{Computable analysis}, Texts in Theoretical Computer
Science. An EATCS Series, Springer-Verlag, Berlin, 2000, An
introduction. MR 1795407 (2002b:03129)

  \end{thebibliography}

\end{frame}
}
\end{document}
